The Unicode Cookbook \linebreak for Linguists

### 2016-08-18 book/chapters/introduction.tex
fixes typo
typos

\subsubsection*{Structure of this bok}

@@

In the nineteenth century, electric telegraphy lead to a new approach
in which written language characters were encoded by signals sent through a
copper wire. Originally, \textsc{bisignal codes} were used, consisting of two
different signals. For example, Carl Friedrich Gauss in 1833 used positive and
negative current \citep[282]{Mania2008}. More famous and influential, Samuel
Morse in 1836 used long and short pulses. In those bisignal codes each character
from the written language was encoded with a different number of signals
(between one and five), so two different separators are needed: one between
signals and one between characters. For example, in Morse-code there is a short
pause between signals and a long pause between characters.\footnote{Actually,
Morse-code also includes an extra long pause between words. Interestingly, it
took a long time to consider the written word boundary---using white-space---as
a bona-fide character that should simply be encoded with its own code point.
This happened only with the revision of the Baudot-code (see below) by Donald
Murray in 1901, in which he introduced a specific white-space code. This
principle has been followed ever since.}

>>>>

\subsubsection*{Structure of this book}

@@

In the nineteenth century, electric telegraphy lead to a next innovation in
which written language characters were encoded by signals sent through a copper
wire. Originally, \textsc{bisignal codes} were used, consisting of two different
signals. For example, Carl Friedrich Gauss in 1833 used positive and negative
current \citep[282]{Mania2008}. More famous and influential, Samuel Morse in
1836 used long and short pulses. In those bisignal codes each character from the
written language was encoded with a different number of signals (between one and
five), so two different separators are needed: one between signals and one
between characters. For example, in Morse-code there is a short pause between
signals and a long pause between characters.\footnote{Actually, Morse-code also
includes an extra long pause between words. Interestingly, it took a long time
to consider the written word boundary---using white-space---as a bona-fide
character that should simply be encoded with its own code point. This happened
only with the revision of the Baudot-code (see below) by Donald Murray in 1901,
in which he introduced a specific white-space code. This principle has been
followed ever since.}
